---
title: "Practice Questions"
date: October 27, 2021
week: 9
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: false
---

```{r setup, include=FALSE}
# Basic knit settings
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  comment = "#>",
  fig.retina = 3,
  fig.path = "figs/"
)

library(tidyverse)
library(here)
```



## Practice Questions 1

Suppose we estimate a model and get the following results:

$$
\hat{\beta} =
\begin{bmatrix}
-0.4
\\ 
0.5
\end{bmatrix}
$$

$$
\nabla_{\beta}^2 \ln(\mathcal{L}) =
\begin{bmatrix}
-6000 & 60
\\ 
60 & -700
\end{bmatrix}
$$

a) Use the hessian to compute the standard errors for $\hat{\beta}$

```{r}
# Write code here
```

b) Use the standard errors to compute a 95% confidence interval around $\hat{\beta}$

```{r}
# Write code here
```



## Practice Questions 2

Suppose we estimate the following utility model describing preferences for cars:

$$
u_j = \alpha p_j + \beta_1 x_j^{mpg} + \beta_2 x_j^{elec} + \varepsilon_j
$$

The estimated model produces the following results:

Parameter | Coefficient
----------|------------
$\alpha$ | -0.7
$\beta_1$ | 0.1
$\beta_2$ | -0.4

Hessian:

$$
\begin{bmatrix}
-6000 & 50 & 60
\\ 
50 & -700 & 50
\\
60 & 50 & -300
\end{bmatrix}
$$

a) Generate 10,000 draws of the model coefficients using the estimated coefficients and hessian. Use the `mvrnorm()` function from the `MASS` library.

```{r}
# Write code here
```

b) Use the draws to compute the mean and 95% confidence intervals of each parameter estimate.

```{r}
# Write code here
```



# In Class Question 1: Long <--> Wide

Write code to read in the following two files:

- `pv_cells.csv`: Data on solar photovoltaic cell production by country
- `milk_production.csv`: Data on milk production by state

```{r}
# Write code here
```

Now modify the format of each:

- If the data are in "wide" format, convert it to "long" with `pivot_longer()`
- If the data are in "long" format, convert it to "wide" with `pivot_wider()`

```{r}
# Write code here
```
