---
title: "Practice Questions"
date: October 27, 2021
week: 9
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: false
---

```{r setup, include=FALSE}
# Basic knit settings
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  comment = "#>",
  fig.retina = 3,
  fig.path = "figs/"
)

library(tidyverse)
library(here)
```



## Practice Questions 1

Suppose we estimate a model and get the following results:

$$
\hat{\beta} =
\begin{bmatrix}
-0.4
\\ 
0.5
\end{bmatrix}
$$

$$
\nabla_{\beta}^2 \ln(\mathcal{L}) =
\begin{bmatrix}
-6000 & 60
\\ 
60 & -700
\end{bmatrix}
$$

a) Use the hessian to compute the standard errors for $\hat{\beta}$

```{r}
hessian <- matrix(c(-6000, 60, 60, -700), ncol = 2, byrow = TRUE)
covariance <- -1*solve(hessian)
se <- sqrt(diag(covariance))
sigma1 <- se[1]
sigma2 <- se[2]
sigma1
sigma2
```

b) Use the standard errors to compute a 95% confidence interval around $\hat{\beta}$

```{r}
beta1 <- -0.4
beta2 <- 0.5
ci1 <- c(beta1 - 2*sigma1, beta1 + 2*sigma1)
ci2 <- c(beta2 - 2*sigma2, beta2 + 2*sigma2)
ci1
ci2
```



## Practice Questions 2

Suppose we estimate the following utility model describing preferences for cars:

$$
u_j = \alpha p_j + \beta_1 x_j^{mpg} + \beta_2 x_j^{elec} + \varepsilon_j
$$

The estimated model produces the following results:

Parameter | Coefficient
----------|------------
$\alpha$ | -0.7
$\beta_1$ | 0.1
$\beta_2$ | -0.4

Hessian:

$$
\begin{bmatrix}
-6000 & 50 & 60
\\ 
50 & -700 & 50
\\
60 & 50 & -300
\end{bmatrix}
$$

a) Generate 10,000 draws of the model coefficients using the estimated coefficients and hessian. Use the `mvrnorm()` function from the `MASS` library.

```{r}
beta <- c(-0.7, 0.1, -4.0)

hessian <- matrix(c(
    -6000,   50,   60,
       50, -700,   50,
       60,   50, -300),
    ncol = 3, byrow = TRUE)

covariance <- -1*solve(hessian)

draws <- MASS::mvrnorm(10^5, beta, covariance)
head(draws)
```

b) Use the draws to compute the mean and 95% confidence intervals of each parameter estimate.

```{r}
# Mean and CI for par 1
mean(draws[, 1])
quantile(draws[, 1], c(0.025, 0.975))

# Compare to computed CI
sigma <- sqrt(diag(covariance))
c(beta[1] - 2*sigma[1], beta[1] + 2*sigma[1])

# Mean and CI for par 2 & 3
mean(draws[, 2])
quantile(draws[, 2], c(0.025, 0.975))
mean(draws[, 3])
quantile(draws[, 3], c(0.025, 0.975))

# Solution using the class package ci() function:
maddTools::ci(draws, ci = 0.95)
```



# In Class Question 1: Long <--> Wide

Write code to read in the following two files:

- `pv_cells.csv`: Data on solar photovoltaic cell production by country
- `milk_production.csv`: Data on milk production by state

```{r}
milk_production <- read_csv(here('data', 'milk_production.csv'))
pv_cells <- read_csv(here('data', 'pv_cells.csv'))
```

Now modify the format of each:

- If the data are in "wide" format, convert it to "long" with `pivot_longer()`
- If the data are in "long" format, convert it to "wide" with `pivot_wider()`

```{r}
# milk_production is in long format - convert to wide
milk_wide <- milk_production %>%
    pivot_wider(
        names_from = state, 
        values_from = milk_produced)
head(milk_wide)

# pv_cells is in wide format - convert to long
pv_cells_long <- pv_cells %>%
    pivot_longer(
        cols = China:World,
        names_to = "country", 
        values_to = "numCells")

# Could also do this
pv_cells_long <- pv_cells %>%
    pivot_longer(
        cols = -Year,
        names_to = "country", 
        values_to = "numCells")

head(pv_cells_long)
```
