---
title: "Practice Question Solutions"
date: November 10, 2021
week: 11
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: false
---

```{r setup, include=FALSE}
# Basic knit settings
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  comment = "#>",
  fig.retina = 3,
  fig.path = "figs/"
)

library(tidyverse)
library(knitr)
library(patchwork)
library(kableExtra)
library(here)
library(logitr)
library(fastDummies)
```

## Practice Questions 1

Suppose we estimate the following utility model describing preferences for cars:

$$
\tilde{u}_j = \alpha p_j + \beta_1 x_j^{\mathrm{mpg}} + \beta_2 x_j^{\mathrm{elec}} + \varepsilon_j
$$

where the variables are

- $p_j$: Price in USD $1,000
- $x_j^{\mathrm{mpg}}$: Fuel economy in miles per gallon
- $x_j^{\mathrm{elec}}$: Variable that takes 1 if the car is an electric car and 0 otherwise

The estimated model produces the following coefficients:

- $\alpha$: -0.7
- $\beta_1$: 0.1
- $\beta_2$: -4.0

a) Use the estimated coefficients to compute the WTP for fuel economy and electric car vehicle type.

```{r}
beta <- c(price = -0.7, mpg = 0.1, elec = -4.0)
wtp <- beta / (-1*beta[1])
wtp
```

b) Use the estimated coefficients to compute market shares for the alternatives in the following market:

<div style="width:200px">
alternative | price | mpg | elec
1 | 15 | 20 | 0
2 | 30 | 100 | 1
3 | 20 | 40 | 0
</div>

```{r}
X <- matrix(c(
    15, 20, 0,
    30, 100, 1,
    20, 40, 0),
    ncol = 3, byrow = TRUE)

v_j <- X %*% beta
exp_v_j <- exp(v_j)
P_j <- exp_v_j / sum(exp_v_j)
P_j
```

Very few people will choose the electric vehicle (option 2). Most will choose the less expensive (and less fuel efficient) gasoline vehicle.




## Practice Questions 2

Suppose we estimate the following utility model describing preferences for cars:

$$
\tilde{u}_j = \alpha p_j + \beta_1 x_j^{\mathrm{mpg}} + \beta_2 x_j^{\mathrm{elec}} + \varepsilon_j
$$

where the variables are

- $p_j$: Price in USD $1,000
- $x_j^{\mathrm{mpg}}$: Fuel economy in miles per gallon
- $x_j^{\mathrm{elec}}$: Variable that takes 1 if the car is an electric car and 0 otherwise

The estimated model produces the following coefficients and hessian:

- $\alpha$: -0.7
- $\beta_1$: 0.1
- $\beta_2$: -4.0

$$
\nabla_{\beta}^2 \ln(\mathcal{L}) =
\begin{bmatrix}
-6000 & 50 & 60
\\
50 & -700 & 50
\\
60 & 50 & -300
\end{bmatrix}
$$

a) Generate 10,000 draws of the model coefficients using the estimated coefficients and hessian. Use the `mvrnorm()` function from the `MASS` library.

```{r}
library(MASS)

beta <- c(price = -0.7, mpg = 0.1, elec=-4.0)
hessian <- matrix(c(
    -6000,   50,   60,
       50, -700,   50,
       60,   50, -300),
    ncol=3, byrow=T)

covariance <- -1*(solve(hessian))
draws <- mvrnorm(10^5, beta, covariance)
head(draws)
```

b) Use the draws to compute the mean WTP and 95% confidence intervals of WTP for fuel economy and electric car vehicle type.

```{r}
wtp_draws <- as.data.frame(draws[,2:3] / (-1*draws[,1]))
head(wtp_draws)

# Fuel economy:
mean(wtp_draws$mpg)
quantile(wtp_draws$mpg, c(0.025, 0.975))

# Electric vehicle type:
mean(wtp_draws$elec)
quantile(wtp_draws$elec, c(0.025, 0.975))

# Other approach, use the ci() function 
maddTools::ci(wtp_draws)
```
