---
title: "Practice Questions"
date: October 20, 2021
week: 8
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: false
---

```{r setup, include=FALSE}
# Basic knit settings
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  comment = "#>",
  fig.retina = 3,
  fig.path = "figs/"
)

library(tidyverse)
library(knitr)
library(patchwork)
library(kableExtra)
library(here)
library(logitr)
library(fastDummies)
```

Consider a box with dimensions $x$, $y$, and $z$ with a volume of 1 cubic meters.

You wish to find the dimensions $x$, $y$, and $z$ of the box that minimizes the total surface area of all 6 faces.

1. Write this optimization problem in negative null form.
2. Using a gradient decent algorithm, write code to find the solution.

The surface area is 

$$
A = 2xy + 2yz + 2zx
$$

The volume is 

$$
V = xyz = 1
$$

Solve volume for $z$ and substitute into surface area:

$$
z = \frac{1}{xy}
$$

$$
A = 2xy + \frac{2}{x} + \frac{2}{y}
$$

1. The problem in negative null form is 

$$
\min_{x,y,z} - 2xy - \frac{2}{x} - \frac{2}{y}
$$

The gradient is:

$$
\Delta f(\underline{x}) = 
\begin{bmatrix}
- 2y + \frac{2}{x^2}
\\ 
- 2x + \frac{2}{y^2}
\end{bmatrix}
$$

```{r}
# Use a loop to compute 20 steps of a gradient descent algorithm:
df <- data.frame(stepNumber = seq(1, 1000), x = 0, y = 0)
x0 <- c(1.5, 1.5)
step <- 0.001
for (i in 1:nrow(df)) {
    x <- x0[1]
    y <- x0[2]
    grad <- c(-2*y + 2/x^2, -2*x + 2/y^2)
    x1 <- x0 - step*grad
    df[i, c('x', 'y')] <- x1
    x0 <- x1
}
df
```
