---
title: "Practice Questions"
date: October 20, 2021
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: false
---

```{r setup, include=FALSE}
# Basic knit settings
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  comment = "#>",
  fig.retina = 3,
  fig.path = "figs/"
)

library(tidyverse)
library(knitr)
library(patchwork)
library(kableExtra)
library(here)
library(logitr)
library(fastDummies)
```

## Practice Questions 1

**Observations** - Height of students (inches):

```{r, echo=FALSE}
x <- c(65, 69, 66, 67, 68, 72, 68, 69, 63, 70)
x
```

a) Let's say we know that the height of students, $\tilde{x}$, in a classroom follows a normal distribution. A professor obtains the above height measurements students in her classroom. What is the log-likelihood that $\tilde{x} \sim \mathcal{N} (68, 4)$? In other words, compute $\ln \mathcal{L} (\mu = 68, \sigma = 4)$.

```{r}
# Write code here
```

b) Compute the log-likelihood function using the same standard deviation $(\sigma = 4)$ but with the following different values for the mean, $\mu: 66, 67, 68, 69, 70$. How do the results compare? Which value for $\mu$ produces the highest log-likelihood?

```{r, fig.height=4, fig.width=6}
# Write code here
```



## Practice Questions 2

Consider the following function:

$$f(x) = x^2 - 6x$$

The gradient is:

$$\nabla f(x) = 2x - 6$$

Using the starting point $x = 1$ and the step size $\gamma =  0.3$, apply the gradient descent method to compute the next **three** points in the search algorithm.

```{r, fig.height=4, fig.width=6}
# Write code here
```




## Practice Questions 3

Consider the following function:

$$
f(\underline{x}) = x_1^2 + 4x_2^2
$$

The gradient is:

$$
\nabla f(\underline{x}) =
\begin{bmatrix}
2x_1
\\
8x_2
\end{bmatrix}
$$

Using the starting point $\underline{x}_0 = [1, 1]$ and the step size $\gamma =  0.15$, apply the gradient descent method to compute the next **three** points in the search algorithm.

```{r, fig.height=4, fig.width=6}
# Write code here
```



## In Class Questions 1

1. Write code to read in the `state_abbs.csv` and `state_regions.csv` data files in the "data" folder.

```{r}
# Write code here
```

2. Create a new data frame called `states` by joining the two data frames `states_abbs` and `state_regions` together. The result should be a data frame with variables `region`, `name`, `abb`.

```{r}
# Write code here
```
