---
title: "Bears Analysis"
author: "John Helveston"
output:
  html_document:
    toc: yes
    toc_float: yes
    theme: flatly
---

```{r setup, include=FALSE}
# Basic knit settings
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  comment = "#>",
  fig.retina = 3,
  fig.path = "figs/"
)

# Load libraries
library(tidyverse)
library(here)

# Read in data 
bears <- read_csv(here::here('data', 'bear_killings.csv'))
```

### Which months have the highest frequency of bear killings?

```{r}
bears %>% 
  count(month) %>% 
  arrange(desc(n))
```

Most attacks occur during the **summer**, with August having the highest number of attacks.

### Who has been killed more often by bears: hunters or hikers?

```{r}
bears %>% 
  count(hunter, hiker)
```

Although *hunters* are killed more often than *hikers*, the vast majority of the data set does not record the hunter / hiker status of the victims. 

### How do the the number of bear attacks on men vs women compare?

```{r}
bears %>% 
  count(gender)
```

Far more attacks have involved men than women. 
