---
title: "Practice with ggplot2"
author: "John Helveston"
output:
  html_document:
    toc: yes
    toc_float: yes
    theme: flatly
---

```{r setup, include=FALSE}
# Basic knit settings
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  comment = "#>",
  fig.retina = 3,
  fig.path = "figs/"
)

# Load libraries
library(tidyverse)
library(here)

# Read in data 
bears <- read_csv(here::here('data', 'bear_killings.csv'))
```

### Where should I put the `aes()` bit? 

If you put it at the "top level" inside `ggplot(aes(...))`, the mapping will apply to all levels. For example: 

```{r, fig.height=4, fig.width=6}
bears %>% 
  count(month) %>%
  ggplot(aes(x = month, y = n)) +
  geom_point() + 
  geom_line()
```

In contrast, if you put the `aes()` mapping inside a single geometry layer, it will only apply to that layer. For example, this will cause an error since the `geom_line()` part doesn't have an aesthetic mapping:

```{r, fig.height=4, fig.width=6, error=TRUE}
bears %>% 
  count(month) %>% 
  ggplot() +
  geom_point(aes(x = month, y = n)) + 
  geom_line()
```

# Main geoms

## `geom_point()`

Basic scatterplot: 

```{r, fig.height=4, fig.width=6}
mpg %>% 
  ggplot() +
  geom_point(aes(x = displ, y = hwy))
```

Change color for all points:

```{r, fig.height=4, fig.width=6}
mpg %>% 
  ggplot() +
  geom_point(aes(x = displ, y = hwy), color = 'blue')
```

To change color based on a variable, map the variable to `color` in `aes()`:

```{r, fig.height=4, fig.width=7}
mpg %>% 
  ggplot() +
  geom_point(aes(x = displ, y = hwy, color = class)) 
```

Map the shape instead of color (usually not a great idea):

```{r, fig.height=4, fig.width=7}
mpg %>% 
  ggplot() +
  geom_point(aes(x = displ, y = hwy, shape = class)) 
```

What happened to SUV?

## `geom_line()` vs. `geom_smooth()`

`geom_line()` connects all the dots:

```{r, fig.height=4, fig.width=6}
mpg %>% 
  ggplot() +
  geom_line(aes(x = displ, y = hwy))
```

The reason this looks messy is because `geom_line()` is trying to literally connect every dot from left to right. 

If you wanted a single "best-fit" trend line, use `geom_smooth()`:

```{r, fig.height=4, fig.width=6}
mpg %>% 
  ggplot() +
  geom_smooth(aes(x = displ, y = hwy))
```

Set `se = FALSE` to drop the error bounds:

```{r, fig.height=4, fig.width=6}
mpg %>% 
  ggplot() +
  geom_smooth(aes(x = displ, y = hwy), se = FALSE)
```

## `geom_col()`

For these examples, I'm creating a smaller summary data frame first that just counts how many rows there are for each class:

```{r}
mpg %>% 
  count(class)
```

Basic bar plot of the counts:

```{r, fig.height=4, fig.width=7}
mpg %>% 
  count(class) %>% 
  ggplot() +
  geom_col(aes(x = class, y = n), width = 0.7) # width is width of bars
```

Re-order bars based on count using `reorder()`:

```{r, fig.height=4, fig.width=7}
mpg %>% 
  count(class) %>% 
  ggplot() +
  geom_col(aes(x = reorder(class, n), y = n), width = 0.7)
```

To change the color for all bars, use `fill` (not `color`):

```{r, fig.height=4, fig.width=7}
mpg %>% 
  count(class) %>% 
  ggplot() +
  geom_col(aes(x = reorder(class, n), y = n), fill = 'blue', width = 0.7)
```

To change color based on a variable, map the variable to `fill` in `aes()`:

```{r, fig.height=4, fig.width=7}
mpg %>% 
  count(class, drv) %>% # Note I had to include drv in the count too 
  ggplot() +
  geom_col(aes(x = reorder(class, n), y = n, fill = drv), width = 0.7) 
```

Use `position = 'dodge'` to change from stacked to side-by-side:

```{r, fig.height=4, fig.width=8}
mpg %>% 
  count(class, drv) %>% # Note I had to include drv in the count too 
  ggplot() +
  geom_col(
    aes(x = reorder(class, n), y = n, fill = drv), 
    position = "dodge", width = 0.7) 
```

# Practice

```{r, fig.height=4, fig.width=7}

```


```{r, fig.height=4, fig.width=6}

```


```{r, fig.height=4, fig.width=6}

```



# Facets

Facets make multiple small charts and are useful when you have many levels in a categorical variable.

For example, this plot has too many color categories for the color to be useful:

```{r, fig.height=4, fig.width=7}
mpg %>%
  ggplot(aes(x = displ, y = hwy)) +
  geom_point(aes(color = class))
```

Instead, we can use `facet_wrap()` to show multiple charts of each vehicle class:

```{r, fig.height=9, fig.width=10}
mpg %>%
  ggplot(aes(x = displ, y = hwy)) +
  geom_point() +
  facet_wrap(~class)
```

You can also use `facet_grid()` to facet by two variables:

```{r, fig.height=7, fig.width=10}
mpg %>%
  ggplot(aes(x = displ, y = hwy)) +
  geom_point() +
  facet_grid(drv ~ cyl)
```



# Extra Practice

```{r, fig.height=5, fig.width=7}
bears %>%
  count(year, gender)
```

```{r, fig.height=4, fig.width=6}
mpg %>%
    mutate(manufacturer = str_to_title(manufacturer)) %>%
    group_by(manufacturer) %>%
    summarise(mean_hwy = mean(hwy))
```
