---
title: "Practice Questions"
date: October 13, 2021
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  comment = "#>",
  fig.retina = 3,
  fig.path = "figs/"
)
library(tidyverse)
library(knitr)
library(here)
library(logitr)
library(fastDummies)
```



## Practice Question 1

a) A random variable, $\tilde{x}$, has the PDF, $f_{\tilde{x}}(x)$. Write the equation to compute its total probability (hint: think area under the curve!). What is the answer to the equation?

b) A random variable, $\tilde{x}$, has a uniform distribution between the values 0 and 1. Draw the probability density function (PDF) and Cumulative Density Function (CDF) of $\tilde{x}$.

c) The value of a random variable, $\tilde{x}$, is determined by rolling one fair, 6-sided dice. Draw the PDF and CDF of $\tilde{x}$.



## Practice Question 2

a) A consumer is making a choice between two bars of chocolate: milk chocolate $(m)$ and dark chocolate $(d)$. Assume that we know the observed utility of each bar to be $v_m = 3$ and $v_d = 4$. Using a logit model, compute the probabilities of choosing each bar: $P_m$ and $P_d$.

```{r}
# Write code here
```

```{r}
# Write code here
```

b) A third bar of chocolate is now added to the choice set. It is the exact same as the milk chocolate bar, but it has a slightly different wrapper (which has no effect on the consumer's utility). Now,  $v_{m1} = v_{m2} = 3$, and $v_d = 4$. Based on the probabilities from question a), what would we expect the probabilities of choosing each bar to be? What probabilities does the logit model produce?

```{r}
# Write code here
```



## Practice Question 3

|Attribute |Bar 1 |Bar 2 |Bar 3 |
|----------|------|------|------|
|Price     |$1.20 |$1.50 |$3.00 |
|% Cacao   |10%   |60%   |80%   |

a) Write out a model for the observed utility of each chocolate bar in the above set.

b) If the coefficient for the _price_ attribute was -0.1 and the coefficient for % _Cacao_ attribute was 0.1, what is the difference in the observed utility between bars 3 and 1?

```{r}
# Write code here
```

c) With the addition of the _brand_ attribute, repeat part a.

|Attribute |Bar 1   |Bar 2 |Bar 3       |
|----------|--------|------|------------|
|Price     |$1.20   |$1.50 |$3.00       |
|% Cacao   |10%     |60%   |80%         |
|Brand     |Hershey |Lindt |Ghirardelli |




# In-Class Questions 1

Let's say our utility function is:

$$v_j = \beta_1 x_j^{\mathrm{price}} + \beta_2 x_j^{\mathrm{cacao}} + \beta_3 \delta_j^{\mathrm{hershey}} + \beta_4 \delta_j^{\mathrm{lindt}}$$

And we estimate the following coefficients:

Parameter | Coefficient
----------|-----------
$\beta_1$ | -0.1
$\beta_2$ | 0.1
$\beta_3$ | -2.0
$\beta_4$ | -0.1

a) What are the expected probabilities of choosing each of these bars using a logit model?

```{r}
# Write your solution here
```

b) What price would Bar 2 have to be to get a 50% market share?

```{r}
# Write your solution here
```








# In-Class Questions 2

1. Run the code chunk to read in the `data.csv` file in the "data" folder.

```{r}
data <- read_csv(here('data', 'data.csv'))
```

2. Write code to estimate the following utility model (HINT: you may need to make some dummy-coded variables!):

$$u_j = \beta_1 x_j^{\mathrm{price}} + \beta_2 x_j^{\mathrm{\%cacao}} + \beta_3 \delta_j^{\mathrm{crispy}} + \beta_4 \delta_j^{\mathrm{hershey}} + \beta_5 \delta_j^{\mathrm{lindt}} + \varepsilon_j$$

```{r}
# Write your solution here
```

3. Write code to plot the change in utility for the _price_ attribute.

```{r}
# Write your solution here
```
