---
title: "Practice Questions"
date: November 17, 2021
week: 12
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: false
---

```{r setup, include=FALSE}
# Basic knit settings
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  comment = "#>",
  fig.retina = 3,
  fig.path = "figs/"
)

library(tidyverse)
library(logitr)
```

## Practice Questions 1

Suppose we estimate the following utility model describing preferences for cars:

$$
\tilde{u}_j = \beta_1 x_j^{\mathrm{price}} + \beta_2 x_j^{\mathrm{mpg}} + \beta_3 x_j^{\mathrm{elec}} + \varepsilon_j
$$

a) Using interactions, write out a model that accounts for differences in the effects of $x_j^{\mathrm{price}}$, $x_j^{\mathrm{mpg}}$, and $x_j^{\mathrm{elec}}$ between two groups: A and B.

**Solution**:


b) Write out the effects of $x_j^{\mathrm{price}}$, $x_j^{\mathrm{mpg}}$, and $x_j^{\mathrm{elec}}$ for each group.

**Solution**:



# Practice Question 2

Suppose we estimate the following utility model describing preferences for chocolate bars between two groups: A & B

$$
\tilde{u}_j = \beta_1 x_j^{\mathrm{price}} + \beta_2 x_j^{\mathrm{caco}} + \beta_3 x_j^{\mathrm{price}}\delta_j^{\mathrm{B}} + \beta_4 x_j^{\mathrm{cacao}}\delta_j^{\mathrm{B}} + \varepsilon_j
$$

The estimated model produces the following coefficients and hessian:

$\beta$ = [-0.7, 0.1, 0.2, 0.8]

$$
H =
\begin{bmatrix}
-6000 & 50 & 60 & 70
\\
50 & -700 & 50 & 100
\\
60 & 50 & -300 & 20
\\
70 & 100 & 20 & -6000
\end{bmatrix}
$$

a) Use the `mvrnorm()` function from the `MASS` library to generate 10,000 draws of the model coefficients.

```{r}
# Write code here
```

b) Use the draws to compute the mean WTP and 95% confidence intervals of the effects of $x_j^{\mathrm{price}}$ and $x_j^{\mathrm{cacao}}$ for each group (A & B).

```{r}
# Write code here
```



# Practice Question 3

a) Use the `logitr` package to estimate the following homogeneous model:

$$
\tilde{u}_j = \beta_1 x_j^{\mathrm{price}} + \beta_2 \delta_j^{\mathrm{feat}} + \beta_3 \delta_j^{\mathrm{dannon}} + \beta_4 \delta_j^{\mathrm{hiland}} +
\beta_5 \delta_j^{\mathrm{weight}} + \varepsilon_j
$$

where the three $\delta$ coefficients are dummy variables for Dannon, Hiland, and Weight Watchers brands (Yoplait is the reference level).

```{r}
# Write code here
```

b) Use the `logitr` package to estimate the same model but with the following mixing distributions:

- $\beta_1 \sim \mathcal{N} (\mu_1, \sigma_1)$
- $\beta_2 \sim \mathcal{N} (\mu_2, \sigma_2)$

```{r}
# Write code here
```
