---
title: "Practice Question Solutions"
date: November 17, 2021
week: 12
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: false
---

```{r setup, include=FALSE}
# Basic knit settings
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  comment = "#>",
  fig.retina = 3,
  fig.path = "figs/"
)

library(tidyverse)
library(logitr)
```

## Practice Questions 1

Suppose we estimate the following utility model describing preferences for cars:

$$
\tilde{u}_j = \beta_1 x_j^{\mathrm{price}} + \beta_2 x_j^{\mathrm{mpg}} + \beta_3 x_j^{\mathrm{elec}} + \varepsilon_j
$$

a) Using interactions, write out a model that accounts for differences in the effects of $x_j^{\mathrm{price}}$, $x_j^{\mathrm{mpg}}$, and $x_j^{\mathrm{elec}}$ between two groups: A and B.

**Solution**:

$$
\tilde{u}_j = \beta_1 x_j^{\mathrm{price}} + \beta_2 x_j^{\mathrm{mpg}} + \beta_3 x_j^{\mathrm{elec}} + \beta_4 x_j^{\mathrm{price}}\delta^\mathrm{B} + \beta_5 x_j^{\mathrm{mpg}}\delta^\mathrm{B} + \beta_6 x_j^{\mathrm{elec}}\delta^\mathrm{B} + \varepsilon_j
$$

b) Write out the effects of $x_j^{\mathrm{price}}$, $x_j^{\mathrm{mpg}}$, and $x_j^{\mathrm{elec}}$ for each group.

**Solution**:

Effect |Group A | Group B 
-------|--------|--------
$x_j^\mathrm{price}$ | $\beta_1$ | $\beta_1 + \beta_4$ 
$x_j^\mathrm{mpg}$ | $\beta_2$ | $\beta_2 + \beta_5$ 
$\delta_j^\mathrm{elec}$ | $\beta_3$ | $\beta_3 + \beta_6$ 



# Practice Question 2

Suppose we estimate the following utility model describing preferences for chocolate bars between two groups: A & B

$$
\tilde{u}_j = \beta_1 x_j^{\mathrm{price}} + \beta_2 x_j^{\mathrm{caco}} + \beta_3 x_j^{\mathrm{price}}\delta_j^{\mathrm{B}} + \beta_4 x_j^{\mathrm{cacao}}\delta_j^{\mathrm{B}} + \varepsilon_j
$$

The estimated model produces the following coefficients and hessian:

$\beta$ = [-0.7, 0.1, 0.2, 0.8]

$$
H =
\begin{bmatrix}
-6000 & 50 & 60 & 70
\\
50 & -700 & 50 & 100
\\
60 & 50 & -300 & 20
\\
70 & 100 & 20 & -6000
\end{bmatrix}
$$

a) Use the `mvrnorm()` function from the `MASS` library to generate 10,000 draws of the model coefficients.

```{r}
beta <- c(b1 = -0.7, b2 = 0.1, b3 = 0.2, b4 = 0.8) 
hessian <- matrix(c(
    -6000, 50, 60, 70,
    50, -700, 50, 100,
    60, 50, -300, 20,
    70, 100, 20, -6000), 
    ncol = 4, byrow = TRUE)
covariance <- -1*(solve(hessian))
draws <- as.data.frame(MASS::mvrnorm(10^5, beta, covariance))
```

b) Use the draws to compute the mean WTP and 95% confidence intervals of the effects of $x_j^{\mathrm{price}}$ and $x_j^{\mathrm{cacao}}$ for each group (A & B).

```{r}
# First, compute the effects for each group
df <- draws %>%
    mutate(
        price_A = b1, 
        cacao_A = b2,
        price_B = b1 + b3, 
        cacao_B = b2 + b4) %>% 
    # I only need to keep the effects (I can drop b1, b2, b3, b4)
    select(starts_with("price"), starts_with("cacao"))
head(df)

# Compute WTP
wtp <- df %>% 
    mutate(
        wtp_cacao_A = cacao_A / (-1*price_A),
        wtp_cacao_B = cacao_B / (-1*price_B)) %>% 
    # I only need to keep the WTP values
    select(starts_with("wtp"))
head(wtp)

# Get a confidence interval
wtp_ci <- maddTools::ci(wtp)
wtp_ci
```



# Practice Question 3

a) Use the `logitr` package to estimate the following homogeneous model:

$$
\tilde{u}_j = \beta_1 x_j^{\mathrm{price}} + \beta_2 \delta_j^{\mathrm{feat}} + \beta_3 \delta_j^{\mathrm{dannon}} + \beta_4 \delta_j^{\mathrm{hiland}} + 
\beta_5 \delta_j^{\mathrm{weight}} + \varepsilon_j
$$

where the three $\delta$ coefficients are dummy variables for Dannon, Hiland, and Weight Watchers brands (Yoplait is the reference level).

```{r}
# First, need to make some dummy coefficients for "brand"
yogurt <- fastDummies::dummy_cols(yogurt, "brand")

model <- logitr(
    data = yogurt, 
    obsID = "obsID", 
    outcome = "choice",
    pars = c("price", "feat", "brand_dannon", "brand_hiland", "brand_weight")
)

summary(model)
```

b) Use the `logitr` package to estimate the same model but with the following mixing distributions:

- $\beta_1 \sim \mathcal{N} (\mu_1, \sigma_1)$
- $\beta_2 \sim \mathcal{N} (\mu_2, \sigma_2)$

```{r}
model_mxl <- logitr(
    data = yogurt, 
    obsID = "obsID", 
    outcome = "choice",
    pars = c("price", "feat", "brand_dannon", "brand_hiland", "brand_weight"),
    randPars = c(price = "n", feat = "n")
)

summary(model_mxl)
```
